\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{sectsty}

\allsectionsfont{\sffamily}
\pagestyle{fancy}
\fancyhf{}
\lhead{MediaReview Social: PRD \& Technical Specification}
\rhead{\today}
\cfoot{\thepage}

\title{MediaReview Social: Product Requirements Document and Technical Specification}
\author{Company Name}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Product Requirements Document (PRD)}

\subsection{Executive Summary}
\textbf{Product Name:} MediaReview Social\\[1mm]
\textbf{Purpose:} A social media platform where users review and discuss movies, TV shows, and various media, enhanced by machine learning for personalized recommendations, sentiment analysis, and content moderation.\\[1mm]
\textbf{Target Audience:} Media enthusiasts, critics, and casual viewers.

\subsection{Product Overview}
\textbf{Description:}\\
MediaReview Social combines social interactions with advanced ML-driven insights. Users can post reviews, engage in discussions, follow trends, and receive personalized media recommendations based on their preferences and review history.

\textbf{Key Value Propositions:}
\begin{itemize}[noitemsep]
    \item \textbf{Community Engagement:} Foster a community of media lovers.
    \item \textbf{Personalization:} Leverage ML to tailor content and recommendations.
    \item \textbf{Quality Insights:} Use sentiment analysis to aggregate user feedback and highlight trending topics.
\end{itemize}

\subsection{Objectives \& Success Metrics}
\textbf{Objectives:}
\begin{itemize}[noitemsep]
    \item Launch an MVP with core review posting, user interaction, and ML-based recommendations.
    \item Achieve high user engagement with at least 10,000 active users in the first three months.
    \item Ensure scalability to support growth and real-time interactions.
\end{itemize}
\textbf{Success Metrics:}
\begin{itemize}[noitemsep]
    \item User sign-up and retention rates.
    \item Average time spent on the platform and review engagement.
    \item Accuracy and user satisfaction with ML recommendations.
    \item System uptime and response times.
\end{itemize}

\subsection{Functional Requirements}
\subsubsection{User Management}
\begin{itemize}[noitemsep]
    \item \textbf{User Registration \& Authentication:} Support email/password and social media logins (e.g., Google, Facebook), password recovery, and multi-factor authentication.
    \item \textbf{Profile Management:} Customizable profiles (profile pictures, bio, review history) with social features (follow system, friend requests, notifications).
\end{itemize}

\subsubsection{Content Creation \& Interaction}
\begin{itemize}[noitemsep]
    \item \textbf{Review Posting:} Ability to create, edit, and delete reviews with ratings (e.g., star rating, thumbs up/down) and support multimedia attachments (images, video clips).
    \item \textbf{Commenting \& Discussions:} Threaded comments, likes, and replies on reviews; ability to share reviews on external social platforms.
    \item \textbf{Feed \& Discovery:} Aggregated content feed with filters (recent, top-rated, trending) and search functionality by media title, genre, or user.
\end{itemize}

\subsubsection{Machine Learning Features}
\begin{itemize}[noitemsep]
    \item \textbf{Recommendation Engine:} Personalized media suggestions based on user behavior and preferences.
    \item \textbf{Sentiment Analysis:} Automated sentiment scoring for reviews (positive, neutral, negative).
    \item \textbf{Content Moderation:} Automated flagging of inappropriate content, spam detection, and alerting for human review.
\end{itemize}

\subsubsection{Media \& API Integration}
\begin{itemize}[noitemsep]
    \item \textbf{External Data Sources:} Integration with media databases (e.g., IMDb, TMDb) for metadata enrichment.
    \item \textbf{API Integrations:} Real-time fetching of media details (cast, synopsis, trailers).
\end{itemize}

\subsection{Non-Functional Requirements}
\begin{itemize}[noitemsep]
    \item \textbf{Performance \& Scalability:} Fast load times, efficient API responses, and scalable infrastructure.
    \item \textbf{Security \& Privacy:} Secure data transmission (HTTPS), encryption, and compliance with GDPR/CCPA.
    \item \textbf{Usability \& Accessibility:} Responsive design, intuitive UI, and adherence to WCAG standards.
    \item \textbf{Maintainability:} Modular codebase, thorough documentation, and automated testing (unit, integration, end-to-end).
\end{itemize}

\subsection{User Stories \& Use Cases}
\begin{itemize}[noitemsep]
    \item \textbf{As a new user:} I want to sign up quickly via email or social media so that I can start posting reviews.
    \item \textbf{As a reviewer:} I want to post reviews with ratings and multimedia to effectively express my opinions.
    \item \textbf{As a reader:} I want to view personalized recommendations and trending reviews to discover new content.
    \item \textbf{As an admin:} I want to moderate content automatically and manually to maintain community standards.
\end{itemize}

\subsection{Roadmap \& Timeline (2-Month Initial Phase)}
\begin{itemize}[noitemsep]
    \item \textbf{Weeks 1--2:} Finalize requirements, select tech stack, and design UX/UI.
    \item \textbf{Weeks 3--4:} Develop backend and frontend MVP; set up databases.
    \item \textbf{Weeks 5--6:} Integrate machine learning features and external APIs.
    \item \textbf{Week 7:} Beta launch, user testing, and performance/security validation.
    \item \textbf{Week 8:} Final bug fixes, production deployment, and post-launch monitoring.
\end{itemize}

\subsection{Risks \& Mitigation}
\begin{itemize}[noitemsep]
    \item \textbf{Scalability Issues:} Early load testing and use of scalable cloud infrastructure.
    \item \textbf{Data Privacy Concerns:} Adherence to data protection regulations and robust security measures.
    \item \textbf{ML Model Accuracy:} Continuous model training with user feedback and performance monitoring.
\end{itemize}

\newpage
\section{Technical Specification Document}

\subsection{System Architecture Overview}
\textbf{Architecture Style:} Microservices-based architecture for modularity and scalability.\\[2mm]
\textbf{Components:}
\begin{itemize}[noitemsep]
    \item \textbf{Frontend:} Web and mobile client applications.
    \item \textbf{Backend:} RESTful (or GraphQL) API server handling user management, content, and ML endpoints.
    \item \textbf{ML Services:} Microservices for recommendation engine, sentiment analysis, and content moderation.
    \item \textbf{Database:} Combination of relational (e.g., PostgreSQL) and NoSQL (e.g., MongoDB) databases.
    \item \textbf{Integration Layer:} API gateways for external media data (IMDb, TMDb).
\end{itemize}

\subsection{Technology Stack}
\textbf{Frontend:}
\begin{itemize}[noitemsep]
    \item Framework: React.js or Vue.js for web; React Native or Flutter for mobile.
    \item State Management: Redux or Vuex.
\end{itemize}

\textbf{Backend:}
\begin{itemize}[noitemsep]
    \item Language/Framework: Node.js (Express/Koa) or Python (Django/Flask).
    \item API: RESTful API or GraphQL.
\end{itemize}

\textbf{Machine Learning:}
\begin{itemize}[noitemsep]
    \item Frameworks: TensorFlow, PyTorch, or scikit-learn.
    \item NLP Libraries: NLTK, spaCy for sentiment analysis.
\end{itemize}

\textbf{Databases:}
\begin{itemize}[noitemsep]
    \item Relational: PostgreSQL for structured data.
    \item NoSQL: MongoDB for unstructured data and caching.
\end{itemize}

\textbf{Deployment \& Infrastructure:}
\begin{itemize}[noitemsep]
    \item Containerization: Docker.
    \item Orchestration: Kubernetes.
    \item Cloud Providers: AWS, Google Cloud, or Azure.
\end{itemize}

\textbf{CI/CD:}
\begin{itemize}[noitemsep]
    \item Tools: GitHub Actions, Jenkins, or CircleCI.
\end{itemize}

\subsection{Detailed System Design}
\subsubsection{API Specifications}
\textbf{Authentication API:}
\begin{itemize}[noitemsep]
    \item Endpoints: \texttt{/api/auth/register}, \texttt{/api/auth/login}, \texttt{/api/auth/recover}.
    \item Methods: POST for registration/login, GET/PUT for profile updates.
\end{itemize}

\textbf{Review API:}
\begin{itemize}[noitemsep]
    \item Endpoints: \texttt{/api/reviews}, \texttt{/api/reviews/\{id\}}.
    \item Methods: GET for fetching reviews, POST for creating reviews, PUT/DELETE for updating/deleting reviews.
\end{itemize}

\textbf{User API:}
\begin{itemize}[noitemsep]
    \item Endpoints: \texttt{/api/users/\{id\}}.
    \item Methods: GET for fetching user data, PUT for profile updates.
\end{itemize}

\textbf{ML API:}
\begin{itemize}[noitemsep]
    \item Endpoints: \texttt{/api/ml/recommendations}, \texttt{/api/ml/sentiment}.
    \item Methods: POST for submitting data for analysis, GET for fetching recommendations.
\end{itemize}

\subsubsection{Database Schema \& Data Flow}
\textbf{User Data Model:}
\begin{itemize}[noitemsep]
    \item Tables/Collections for Users, Profiles, Followers, and Authentication tokens.
\end{itemize}

\textbf{Review Data Model:}
\begin{itemize}[noitemsep]
    \item Tables/Collections for Reviews, Comments, Ratings, and Media Attachments.
\end{itemize}

\textbf{ML Data Pipeline:}
\begin{itemize}[noitemsep]
    \item \textbf{Data Ingestion:} Collect user interactions and review text.
    \item \textbf{Processing:} Preprocess data (tokenization, normalization) for ML models.
    \item \textbf{Storage:} Maintain historical data for retraining models.
\end{itemize}

\subsubsection{Machine Learning Pipeline}
\textbf{Recommendation Engine:}
\begin{itemize}[noitemsep]
    \item \textbf{Data:} User behavior logs and review history.
    \item \textbf{Model:} Collaborative filtering combined with content-based filtering.
    \item \textbf{Deployment:} Exposed as a RESTful service.
\end{itemize}

\textbf{Sentiment Analysis:}
\begin{itemize}[noitemsep]
    \item \textbf{Data:} Text from reviews.
    \item \textbf{Model:} Pre-trained NLP model fine-tuned for sentiment classification.
    \item \textbf{Integration:} Run inference on review submission and update sentiment scores.
\end{itemize}

\textbf{Content Moderation:}
\begin{itemize}[noitemsep]
    \item \textbf{Data:} User-generated content.
    \item \textbf{Model:} Classifier for spam and offensive language detection.
    \item \textbf{Process:} Flag content and queue for human review if necessary.
\end{itemize}

\subsubsection{Security \& Privacy}
\begin{itemize}[noitemsep]
    \item \textbf{Authentication \& Authorization:} Secure token-based authentication (JWT) and role-based access control.
    \item \textbf{Data Protection:} Encryption in transit (TLS/SSL) and at rest.
    \item \textbf{Compliance:} Adherence to GDPR, CCPA, and other data protection laws.
\end{itemize}

\subsubsection{Scalability, Performance \& Monitoring}
\begin{itemize}[noitemsep]
    \item \textbf{Scalability:} Microservices architecture with load balancers and auto-scaling groups.
    \item \textbf{Performance Optimization:} Caching strategies (Redis, CDN for static assets), efficient database queries, and indexing.
    \item \textbf{Monitoring:} Logging (ELK stack), monitoring (Prometheus, Grafana), real-time alerts, and error tracking.
\end{itemize}

\subsubsection{Testing \& Deployment}
\begin{itemize}[noitemsep]
    \item \textbf{Testing:} Automated unit, integration, and end-to-end tests; performance and load testing.
    \item \textbf{Deployment Strategy:} CI/CD pipelines, staging environment, rollback plans, and disaster recovery.
\end{itemize}

\newpage
\section{Cost Estimation}
\begin{itemize}[noitemsep]
    \item \textbf{Frontend Hosting \& CDN:} \$50--\$100/month.
    \item \textbf{Backend Servers \& API Services:} \$100--\$200/month.
    \item \textbf{Databases:} \$50--\$100/month.
    \item \textbf{Machine Learning Services:} \$100--\$300/month.
    \item \textbf{Additional Services (Monitoring, Logging, etc.):} \$50--\$100/month.
\end{itemize}

\end{document}
